---
title: "Experimental Design"
author: "Adriana Souza"
date: "June 15, 2018"
output:
   pdf_document:
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1 Goals:

## **Constrain treatment number, size and distribution in the context of permitting requirements and logistical matters.**

```{r loading data}
#plots <- read.csv("plots.csv")
```

## **Conduct power analysis for deliverables based on proposed experimental design, inventory practices and preliminary data.**^[
Do both 1 & 2 using annotated code in a version controlled format]

```{r}
#Loading pwr package
library(pwr)
# n=9 for our 9 plots, two tailed
pwr.t.test(n= 9,d=.5,sig.level=0.05, power = NULL, alternative="two.sided", type="two.sample")
```


# Part 2 Goals:

## Constrain experimental design based on expected mulch volume, permit limits for fill and effective mulch depths

### Estimate total volume of invasive plant biomass on spoil ridges
### Estimate area corresponding to 25 cubic yards of fill in treatment ditch
### Estimate depth of remaining mulch spread onto ridges
### Propose scenarios for removal

# Part 3 Goals:

## Assess adequacy of proposed vegetation inventory elements:

### Element 1: plot size

1. Impact on biomass estimation error
2. Impact on seedling diversity estimation error

### Element 2: plot distribution per treatment

1. Impact on removal / mulch treatment effect estimation error
